Data Cleaning logbook

### 2019-02-21 docs/SupplementaryMaterial.Rmd
Updated MS

```{r eval = T}
invert %>% 
  group_by(ano, comunidad, zona, sitio, transecto) %>%
  count() %>%
  group_by(comunidad, zona) %>%
  count() %>% 
  spread(zona, nn) %>% 
  knitr::kable(caption = "Number of invertebrate transects performed in each site of each community.",
               col.names = c("Community", "Control", "Reserve"),
               booktabs = T)
```

@@

```{r}
fish %>% 
  group_by(ano, comunidad, zona, sitio, transecto) %>%
  count() %>%
  group_by(comunidad, zona) %>%
  count() %>% 
  spread(zona, nn) %>% 
  knitr::kable(caption = "Number of fish transects performed in each site of each community.",
               col.names = c("Community", "Control", "Reserve"),
               booktabs = T)
```

>>>>

```{r eval = T}
invert %>% 
  group_by(ano, comunidad, zona, sitio, transecto) %>%
  count() %>% 
  ungroup() %>% 
  group_by(comunidad, zona) %>%
  count() %>% 
  ungroup() %>% 
  spread(zona, nn) %>% 
  mutate(age = c(10, 4, 4)) %>% 
  knitr::kable(caption = "Number of invertebrate transects performed in each site of each community.",
               col.names = c("Community", "Control", "Reserve", "Years of monitoring"),
               booktabs = T)
```

@@

```{r}
fish %>% 
  group_by(ano, comunidad, zona, sitio, transecto) %>%
  count() %>% 
  ungroup() %>% 
  group_by(comunidad, zona) %>%
  count() %>% 
  ungroup() %>% 
  spread(zona, nn) %>% 
  mutate(age = c(10, 4, 4)) %>% 
  knitr::kable(caption = "Number of invertebrate transects performed in each site of each community.",
               col.names = c("Community", "Control", "Reserve", "Years of monitoring"),
               booktabs = T)
```

### 2019-02-21 scripts/data_cleaning_logbook.Rmd
Updated MS

---
title: "Data Cleaning logbook"
author: "Juan Carlos Villaseñor-Derbez"
date: "last compilation: `r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
---

>>>>

---
title: "Data Cleaning logbook"
author: "Juan Carlos Villaseñor-Derbez"
date: "last compilation: `r Sys.Date()`"
output:
  html_document:
    toc: yes
    # toc_float: yes
---
